\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2021-01-20 sections/methods.tex
Add: "pvalue merging" details to methods section

  \begin{equation*}
    N = \begin{bmatrix}
     edge_{1,1} & edge_{2,1} & \cdots  & edge_{n, 1} \\ 
     edge_{1,2} & edge_{2,2} & \cdots  & edge_{n, 2} \\ 
     \vdots & \vdots & \vdots  & \vdots \\ 
     edge_{1,n} & edge_{2,n} & \cdots  & edge_{n, n}
    \end{bmatrix}      
  \end{equation*}

@@

>>>>

 The merged table $N$ with $p$ edges and $n$ networks, where, each column $N_j$ is the vector representation of one of the networks, each row $L_i$ is the vector representation of one particular edge in all networks (assigned a value of 0 if the edge did not exist in the network but in other networks), and each element $E_{i,j}$ belongs to edge $L_i$ and network $N_j$.

  \begin{equation*}
   N_{p \times n} =
   \begin{bmatrix}
     L_1 \\
     L_2 \\
     \vdots \\
     L_p
   \end{bmatrix}
   =
   \begin{bmatrix}
     E_{1,1} & E_{1,2} & \cdots  & E_{1, n} \\
     E_{2,1} & E_{2,2} & \cdots  & E_{2, n} \\
     \vdots & \vdots & \vdots  & \vdots \\
     E_{p,1} & E_{p,2} & \cdots  & E_{p, n}
   \end{bmatrix}
  \end{equation*}

@@

  \subsection*{Consensus Network and p-value merging}
  \vspace{-5mm}
  Let there be $k$ p-values, denoted by $P_i$, generated from $k$ different methods.

  Fisher~\cite{fisher_224a_1948} proposed that for $k$ independent p-values, the statistic $\Psi$:
  \begin{equation*}
    \Psi = \sum_{i=1}^k -2 \log \left( P_i \right)
    \Psi \sim \chi^2_{2k}
  \end{equation*}

  Brown~\cite{brown_400_1975} extended Fisher's method to dependent p-values by using a re-scaled $\chi^2$ distribution:
  \begin{equation*}
    \Psi \sim c \chi^2_{2f}
  \end{equation*}
  where, $f$ is the degrees of freedom and $c$ is the scale factor and are given by:
  \begin{equation*}
    f = \frac{\mathrm{E}[\Psi]^2}{\mathrm{Var}[\Psi]} ~~~\text{and}~~~ c = \frac{\mathrm{Var}[\Psi]}{2\mathrm{E}[\Psi]} = \frac{k}{f}
  \end{equation*}

  Furthermore, Brown showed that $\mathrm{E}[\Psi]$ and $\mathrm{Var}[\Psi]$ can be calculated directly via a numerical integration:
  \begin{equation*}
    \mathrm{E}[\Psi] = 2k ~~~\text{and}~~~ \mathrm{Var}[\Psi] = 4k + 2\sum_{i<j} \mathrm{Cov} \left( -2\log(P_i), -2\log(P_j) \right)
  \end{equation*}

  Kost and McDermott~\cite{kost_combining_2002} further fit a third-order polynomial to approximate the covariance
  \begin{equation*}
    \mathrm{Cov} \left( -2\log(P_i), -2\log(P_j) \right) \approx 3.263 \rho_{ij} + 0.710 \rho_{ij}^2 + 0.027 \rho_{ij}^3
  \end{equation*}
  where, $\rho_{ij}$ is the correlation between method $i$ and method $j$

  The final combined p-value is then given by:
  \begin{equation*}
    P_{combined} = 1.0 - \Phi_{2f}\left( \psi / c \right)
    \text{where},~ $\psi = -2 \sum_{i=1}^k \log(P_i) ~~~\text{and}~~~ \Phi_{2f} = \mathrm{CDF}\left( \chi^2_{2f} \right)
  \end{equation*}
